An efficient contact value approach to approximating the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-07-07 papers/pair-correlation/paper.tex
fix wording issue pointed out by Jeff Tested on bennet. Took 0:18.77.

\section{Making the CVA efficient}
The existing approaches to approximating the pair correlation function
outlined in Section~\ref{sec:gn} have not been widely used in the
construction of density functionals based on thermodynamic
perturbation theory, largely due to their computational complexity.
While our CVA as described in the previous section is, in terms of
accuracy, an incremental improvement over these existing approaches,
it makes significant gains in terms of computational efficiency,
allowing for its more managable use in such a construction.  We
address the issue by developing a \emph{separable} fit to the radial
distribution function of the hard-sphere fluid (see
Section~\ref{sec:separable-fit} for details).  This separable fit is
of the form
\begin{align}
  g_S(|r_{12}|, g_\sigma) &= \sum_{i} a_i(r_{12}) b_i(g_\sigma)
\end{align}
where the notable aspect is that the radial distribution function is
written as a sum of terms that are each a simple product of a function
of radius with a function of $g_\sigma$.  This enables us to write
typicaly \jeffsays{'typical?' maybe just 'integrals'} integrals
involving the pair distribution function as a summation of
fixed-kernel convolutions, which may be efficiently computed using
Fast Fourier Transforms (FFTs), in $\mathcal{O}(N\log N)$ time.

>>>>

\section{Making the CVA efficient}
The existing approaches to approximating the pair correlation function
outlined in Section~\ref{sec:gn} have not been widely used in the
construction of density functionals based on thermodynamic
perturbation theory, largely due to their computational complexity.
While our CVA as described in the previous section is, in terms of
accuracy, an incremental improvement over these existing approaches,
it makes significant gains in terms of computational efficiency,
allowing for its more managable use in such a construction.  We
address the issue by developing a \emph{separable} fit to the radial
distribution function of the hard-sphere fluid (see
Section~\ref{sec:separable-fit} for details).  This separable fit is
of the form
\begin{align}
  g_S(|r_{12}|, g_\sigma) &= \sum_{i} a_i(r_{12}) b_i(g_\sigma)
\end{align}
where the notable aspect is that the radial distribution function is
written as a sum of terms that are each a simple product of a function
of radius with a function of $g_\sigma$.  This enables us to write
integrals that are linear in the pair distribution function---such as
Eq.~\ref{eq:mean-field}---as a summation of fixed-kernel convolutions,
which may be efficiently computed using Fast Fourier Transforms
(FFTs), in $\mathcal{O}(N\log N)$ time.
